Federated Imputation

### 2020-06-18 Format.Rmd
added setup

>>>>

## Simple evaluation

1. Impute `boys` data with `m=1` to obtain `boyscompl`
2. For `i` repetitions, store as a list `out` the result of

  - partition `boyscompl` into `p=5` parts
  - synthesize the `p` parts
  - combine the `p` synthetic parts into `boyssynth`

3. For the `i` elements in list `out`, evaluate

  - Qbar (e.g regression estimates of `bmi ~ age + wgt`)
  - CI of Qbar
  - coverage of the CI of Qbar

### If method is valid
Then Qbar is unbiased and confidence valid (i.e. at least 95% of CI's cover the population value)
